\documentclass[11pt,letterpaper,oneside,reqno]{article}
\usepackage[top=2.5cm,bottom=2.5cm,left=2.5cm,right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{float,graphicx}
\usepackage{natbib}

\usepackage{fourier}

%\usepackage{stix}
%\usepackage{ccfonts,eulervm}
%\usepackage[T1]{fontenc}
\renewcommand{\rmdefault}{put}
%\geometry{letterpaper}
\usepackage[parfill]{parskip}

%\usepackage[intlimits]{amsmath}

\usepackage{setspace}
\usepackage{amsthm}
\usepackage{appendix}

%\usepackage{fancyvrb}
%\usepackage{supertabular}

\usepackage[font={bf,footnotesize},textfont=md,margin=30pt,aboveskip=0pt,belowskip=0pt]{caption}

\usepackage{lastpage}

\DeclareCaptionLabelFormat{appcaption}{#1 \oldthesection-#2}
\setlength{\headheight}{15pt}

\renewcommand{\topfraction}{0.9}    % max fraction of floats at top
    \renewcommand{\bottomfraction}{0.8} % max fraction of floats at bottom
    %   Parameters for TEXT pages (not float pages):
    \setcounter{topnumber}{2}
    \setcounter{bottomnumber}{2}
    \setcounter{totalnumber}{4}     % 2 may work better
    \setcounter{dbltopnumber}{2}    % for 2-column pages
    \renewcommand{\dbltopfraction}{0.9} % fit big float above 2-col. text
    \renewcommand{\textfraction}{0.07}  % allow minimal text w. figs
    %   Parameters for FLOAT pages (not text pages):
    \renewcommand{\floatpagefraction}{0.7}  % require fuller float pages
    % N.B.: floatpagefraction MUST be less than topfraction !!
    \renewcommand{\dblfloatpagefraction}{0.7}   % require fuller float pages

\newenvironment{myenumerate}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}{\end{enumerate}
}
\newenvironment{myitemize}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}{\end{itemize}
}
\usepackage[uline]{hhtensor}
\usepackage{ctable}
%\usepackage{fancyhdr}
\usepackage{listings}

%\usepackage[style=asceish,sorting=nyt,natbib=true]{biblatex}
%\bibliography{capstone_figparts}

\usepackage[pdftex,bookmarks,colorlinks,breaklinks,pdfpagelabels]{hyperref}

\hypersetup{linkcolor=black,citecolor=black,filecolor=black,urlcolor=black}
%\bibliographystyle{ascelike}
%\bibliographystyle{apalike}
%\bibpunct{[}{]}{;}{a}{}{,}
\newcommand{\p}{\partial}
\newcommand{\del}{\nabla}
\renewcommand{\deg}{^\circ}
\newcommand{\comp}{\overline}
\newcommand{\dd}{\; \mathrm{d}}

%
%%%%%%%%%%%%%% Title and TOC %%%%%%%%%%%%%%%%%%%
%

\begin{document}
\centerline{\Large \bf Wave Modeling, Monitoring, and Analysis} 
\centerline{\Large \bf for PG\&E WaveConnect Pilot Project}
\centerline{Colin Sheppard; Nir Berezovsky; Charlie Sharpsteen;}
\centerline{Jim Zoellick; Charles Chamberlin}
\centerline{Schatz Energy Research Center}
\bigskip
\bigskip

\noindent {\bf Subject:} Progress Report

\noindent {\bf To:} Brendan Dooher, PG\&E

\noindent {\bf Submitted by:} Colin Sheppard

\noindent {\bf Date:} December 7, 2010 

%\noindent {\bf Attachments:} Current draft of overall project report.

\textbf{Activity to Date}\\
Since the last submitted progress report (Septembrer 23, 2010), the team from the Schatz Energy Research Center (SERC) has engaged in the following activities in pursuit of the project goals:
\begin{itemize}
\item Attended Ocean Renewable Energy Conference, September 28-30 in Portland.
\item Finalized configuration of CMS and determination of input formats.
\item Continued to develop model control scripts capable of controling CMS model (work still incomplete).
\item Corrected several issues with the bathymetric data set (for Humboldt domain): standardized the x,y coordinates of all data to a common projection and transformed the vertical datums to mean sea level.
\item Updated the buoy data harvest script to transform spectral wave data from NOAA format (as coefficients) into directional spectra.
\item Developed code for extracting results from CMS output to be inserted into the database (work still incomplete).
\item Created deployment scripts for Ubuntu Linux capable of downloading and installing packages, source code, and the database necessary to run CMS (work still incomplete).
\item Continued development of Matlab classes capable of retreiving, representing, and visualizing model results (work still incomplete).
\item Developed html documentation for several Python modules as well as the GIS resources used in the project.
\end{itemize}

\textbf{Upcoming Activity}\\
We intend to accomplish the following in the month of December (pending funding from PG\&E):
\begin{itemize}
\item Complete development of model control scripts capable of controling CMS model.
\item Complete code for extracting results from CMS output to be inserted into the database.
\item Complete development of Matlab classes for retreival and visualization of model results.
\end{itemize}

\end{document}
