\documentclass[11pt,letterpaper,oneside,reqno]{article}
\usepackage[top=2.5cm,bottom=2.5cm,left=2.5cm,right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{float,graphicx}
\usepackage{natbib}

\usepackage{fourier}

%\usepackage{stix}
%\usepackage{ccfonts,eulervm}
%\usepackage[T1]{fontenc}
\renewcommand{\rmdefault}{put}
%\geometry{letterpaper}
\usepackage[parfill]{parskip}

%\usepackage[intlimits]{amsmath}

\usepackage{setspace}
\usepackage{amsthm}
\usepackage{appendix}

%\usepackage{fancyvrb}
%\usepackage{supertabular}

\usepackage[font={bf,footnotesize},textfont=md,margin=30pt,aboveskip=0pt,belowskip=0pt]{caption}

\usepackage{lastpage}

\DeclareCaptionLabelFormat{appcaption}{#1 \oldthesection-#2}
\setlength{\headheight}{15pt}

\renewcommand{\topfraction}{0.9}    % max fraction of floats at top
    \renewcommand{\bottomfraction}{0.8} % max fraction of floats at bottom
    %   Parameters for TEXT pages (not float pages):
    \setcounter{topnumber}{2}
    \setcounter{bottomnumber}{2}
    \setcounter{totalnumber}{4}     % 2 may work better
    \setcounter{dbltopnumber}{2}    % for 2-column pages
    \renewcommand{\dbltopfraction}{0.9} % fit big float above 2-col. text
    \renewcommand{\textfraction}{0.07}  % allow minimal text w. figs
    %   Parameters for FLOAT pages (not text pages):
    \renewcommand{\floatpagefraction}{0.7}  % require fuller float pages
    % N.B.: floatpagefraction MUST be less than topfraction !!
    \renewcommand{\dblfloatpagefraction}{0.7}   % require fuller float pages

\newenvironment{myenumerate}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}{\end{enumerate}
}
\newenvironment{myitemize}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}{\end{itemize}
}
\usepackage[uline]{hhtensor}
\usepackage{ctable}
%\usepackage{fancyhdr}
\usepackage{listings}

%\usepackage[style=asceish,sorting=nyt,natbib=true]{biblatex}
%\bibliography{capstone_figparts}

\usepackage[pdftex,bookmarks,colorlinks,breaklinks,pdfpagelabels]{hyperref}

\hypersetup{linkcolor=black,citecolor=black,filecolor=black,urlcolor=black}
%\bibliographystyle{ascelike}
%\bibliographystyle{apalike}
%\bibpunct{[}{]}{;}{a}{}{,}
\newcommand{\p}{\partial}
\newcommand{\del}{\nabla}
\renewcommand{\deg}{^\circ}
\newcommand{\comp}{\overline}
\newcommand{\dd}{\; \mathrm{d}}

%
%%%%%%%%%%%%%% Title and TOC %%%%%%%%%%%%%%%%%%%
%

\begin{document}
\centerline{\Large \bf Wave Modeling, Monitoring, and Analysis} 
\centerline{\Large \bf for PG\&E WaveConnect Pilot Project}
\centerline{Colin Sheppard; Nir Berezovsky; Charlie Sharpsteen;}
\centerline{Jim Zoellick; Charles Chamberlin}
\centerline{Schatz Energy Research Center}
\bigskip
\bigskip

\noindent {\bf Subject:} Progress Report

\noindent {\bf To:} Brendan Dooher, PG\&E

\noindent {\bf Submitted by:} Colin Sheppard

\noindent {\bf Date:} August 18, 2010 

\noindent {\bf Attachments:} Current draft of overall project report.

\textbf{Activity to Date}\\
Since the start of the contract term (May 2010), the team from the Schatz Energy Research Center (SERC) has engaged in the following activities in pursuit of the project goals:
\begin{itemize}
\item Research and review of relevant literature (wave/current modeling, x-band radar monitoring of wave spectra, statistical methods) 
\item Research and procurement of necessary equipment and software (multi-core, high performance computer, Matlab + related toolboxes)
\item Deliberation and decision to use the Army Corps. Coastal Modeling System (CMS) as the foundation of the wave modeling effort
\item Development of data harvesting software to retrieve inputs to the model
\item Development/debugging of the CMS-Unix source code to accommodate recent changes in data formats 
\item Packaged NDBC buoy harvesting software for use by Brendan Dooher for 100-year return analysis of wind data.
\end{itemize}

\textbf{Upcoming Activity}\\
We intend to accomplish the following in the coming weeks (along with expected time horizon until completion):
\begin{itemize}
\item Finalize configuration of CMS and determination of input formats (\texttildelow 2 weeks).
\item Use data retrieval scripts to download all available data relevant to our modeling effort (\texttildelow 2 weeks).
\item Complete acquisition of computer hardware for use in model execution (\texttildelow 3 weeks).
\item Organize travel arrangements to Ocean Renewable Energy Conference, September 28-30 in Portland (\texttildelow 3 weeks).
\item Develop model control scripts in Matlab (\texttildelow 4 weeks).
\item Conduct runs for preliminary resource estimation for the Humboldt domain (\texttildelow 6 weeks).
\end{itemize}


\end{document}
